Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2023-11-05 lqg-strings.tex
AddedCommands
SwappedPositionOfInternalIndicesForXFields

\newcommand{\Cyl}{\mathrm{Cyl}}
%%% END Custom commands %%%

@@

Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vierbein fields $E_\mu^I$. Further we will require that the bulk connection and the bulk vierbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$. In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega_a^i$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued one-form fields $X^\mu_I$. However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega_a^i$, we can replace $X^\mu_I$ with $X^\mu_i$.
\begin{equation}\label{eqn:lqg-string-action}
	S_{PA} = -\frac{T}{2} \int d\tau \wedge d\sigma\,e\,e^a_i\,e^b_j \, D_a X^\mu_i D_b X^\nu_j E_\mu^I E_{\nu I},
\end{equation}
where $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
\begin{equation}\label{eqn:worldsheet-deriv}
	D_a X^\mu_i = \partial_a X^\mu_i + \omega_{a\,i}{}^j X^\mu_j,
\end{equation}
where $\omega_{a\,i}{}^j$ is the pullback of the bulk connection to the worldsheet.

>>>>

\newcommand{\Cyl}{\mathrm{Cyl}}

%Luigi's custom commands
\newcommand{\R}{\mathbb{R}}
\newcommand{\diff}{\mathrm{d}}
\newcommand{\inp}{\mathrm{i}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\Lagr}{\mathscr{L}}
\newcommand{\PS}{\mathcal{P}}
%%% END Custom commands %%%

@@

Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$. Further we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega_a^i$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$. In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega_a^i$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu I}$. However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega_a^i$, we can replace $X^{\mu I}$ with $X^{\mu i}$.
\begin{equation}\label{eqn:lqg-string-action}
	S_{PA} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma\,e\,e^a_i\,e^b_j \, D_a X^{\mu i} D_b X^{\nu j} E_\mu^I E_{\nu I},
\end{equation}
where $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
\begin{equation}\label{eqn:worldsheet-deriv}
	D_a X^{\mu i} = \partial_a X^{\mu i} + \omega_{a\,j}^i X^{\mu j},
\end{equation}
where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.
